---
title: "ipaconf2016"
author: "Dasapta Erwin Irawan dan Prana Ugi"
date: "February 6, 2016"
output: pdf_document
---


    Title of Paper
    Author Names, Affiliation, Addresses, Phone number, Fax, E-mail contact
    Designate which Author will present the paper (presenter’s name)
    Indicate preference for (a) Oral), (b) Poster Presentation, (c) Either
    Indicate if this paper was previously presented or published; if so, when, where, and by whom?
    The abstract should encourage the committee to select your paper. It should point out ways that the reader can use your conclusions. The abstract should: (a) state the scope and principle objectives, (b) methods utilized, (c) summarize the results, (d) state the principal conclusions, and (e) Keywords.
    Abstract should be between 150 words and maximum 300 words in length and should be able to stand alone as a short version of the paper.


```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
